\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{quantumBR - Constitution}
\author{Justin Woodring, Jason Phan, Charles Beam}
\date{Oct 30, 2023}                                           % Activate to display a given date or no date

\begin{document}
\maketitle

\section{ARTICLE I - quantumBR} 
\subsection{Club Name}
The name of this club shall be quantumBR.

\section{ARTICLE II - Purpose of Club}
\subsection{Mission}
We are an organization dedicated to fostering and sharing knowledge to educate our peers and make quantum computing accessible to everyone. quantumBR will host information sessions, lectures, hands-on workshops, and student-community collaborative projects.
\subsection{Operation}
This club will operate as an independent entity working within the Louisiana State University subject to the values and policies of the university.
\subsection{Scope}
The scope of this club is not limited to Louisiana State University and it is open to and intended the impact the whole of Louisiana with an emphasis on the greater BR area.
\subsection{Goals}
quantumBR will enhance the educational, recreational, social, or cultural environment of Louisiana State University by being inclusive to all students, by transferring knowledge to students, by forging closer relationships between students and local businesses in the community, and by promoting diversity in the tech community.

\section{ARTICLE III - MEMBERSHIP}
\subsection{Definition of Membership}
Membership will carry no dues and no distinction shall be made between frequent attendees and actual members with exception that members must be LSU students and be in good academic standing.

\section{ARTICLE IV - QUALIFICATION AND ELECTION OF OFFICERS}
\subsection{Qualification}
Club officers must be currently enrolled, have a minimum of a 3.0 cumulative Grade Point Average (GPA), have a current LSU tiger card, and must not be on academic or social probation.
\subsection{Election Date}
The election of the Club Officers shall be held during the Ninth (9th) week of the Spring Semester.
\subsection{Voting Procedure}
Club Officers shall be elected by a simple majority vote of active Club Members present at that Club Meeting. In the event that there are three (3) or more candidates and no one person receives a simple majority of votes then the top two (2) candidates will participate in a run-off election.
\subsection{Elector Eligibility}
The election will be done by secret ballot by attendees who have attended at least four meetings.


\section{ARTICLE V - DUTIES OF THE OFFICERS}
\subsection{President}
Is the official spokesperson of the organization and provides directions for all components of the organization in a manner consistent with the organization’s constitution and policies.
\subsection{Vice President}
Oversees events organized by the group and is in charge of developing and enhancing the delivery of member services.
\subsection{Treasurer}
Oversees the organization’s finances for the benefit of members and the campus community.

\section{ARTICLE VI - EXECUTIVE COUNCIL}
\subsection{Members of the Executive Council}
The Executive Council will consist of the President, Vice President, and Treasurer.

\subsection{Duties of the Executive Council}
\begin{itemize}
\item{To formulate policy of the club between regular meetings and in case of emergencies, subject to the approval of the general membership.}
\item{To execute policies determined by the general membership.}
\item{To govern activities of the club.}
\item{To compile agenda for general meetings.}
\end{itemize}

\section{ARTICLE VII - IMPEACHMENT/REMOVAL AND REPLACEMENT
OF OFFICERS AND MEMBERS}
\subsection{Impeachment Requirements}
All elected officers and club members may be subjected to impeachment and removal by a two-thirds majority vote of the total membership.
\subsection{Grounds for Impeachment}
Grounds for impeachment are negligence and any form of misconduct which is damaging to the club.  An officer/member may be impeached/removed only under the following conditions: there must be a quorum present during impeachment/removal; two-thirds of the membership must vote; prior to impeachment/removal, there must be one week's notice of intent publicized.
\subsection{Vacancy}
Any officer vacancies shall be filled by an election held within two weeks.


\section{ARTICLE VIII - MEETINGS}
\subsection{Public Notice}
There must be public notice of club meetings on the club board at least five (5) school days in advance.
\subsection{Minimum Meeting Requirement}
There must be a meeting at least once a month held at Louisiana State University.
\subsection{Quorum Requirement}
There must be a quorum (a quorum is 50 percent plus 1 of the active or dues-paying membership) present in order to take care of financial action.
\subsection{Financial Minutes}
Minutes must be kept of all financial action with the club’s Treasurer.

\section{ARTICLE IX - RESPONSIBILITIES}
\subsection{Financial Responsibility}
This club accepts full financial responsibility for all activities that bear its name as official sponsor, and will adhere to college regulations.  All publicity for an event must bear the name of the sponsoring club.

\section{ARTICLE X - RIGHT TO ACT}
\subsection{Right to Incur Club Debt}
Any club officer, club member does not have the right to incur any debt or become involved in any business under the title or by implying the title of a club in any way unless given full authority to do so by the club.

\section{ARTICLE XI – AMENDMENTS TO CONSTITUTION}
\subsection{Two-Thirds Requirement}
Any amendment change requires a two-thirds vote at a general club meeting by attendees who have been present for 4 or more meetings.

%\section{}
%\subsection{}
\end{document}  
